Sparse Representation Approaches for First Stage Retrieval: A Review

### 2022-01-09 src/article.tex
Fix indentation.
Add training paragraph for RepBERT.

    \paragraph{Joint loss function.}
    The importance predictor and gating controller are trained jointly because the supervisory
    ranking signal can also be leveraged to guide the training of the gating controller:
    \begin{equation}
        L = L_{rank} + L_{exp}
    \end{equation}\\

@@

    This approach does not use binary gating as in SparTerm, and instead learn model (Equation
    \ref{eqn:splade:importance}) jointly optimizing ranking and regularization losses:
    \begin{equation}
        L = L_{rank-IBN} + \lambda_q L^q_{reg} + \lambda_d L^d_{reg}
    \end{equation}
    where $L_{reg}$ is a sparse regularisation ($L_1$ or $L_{FLOPS}$), $\lambda_q$ and
    $\lambda_d$ are tunable hyper-parameters to control the sparsity of the query and the
    document. \newline

    \paragraph{Training.}
    The models are initialized with the BERT-base pre-trained models.
    Adam optimizer is selected with the learning rate $2 \cdot 10^{-5}$, linear scheduling,
    a warmup of 6000 steps and a batch size of 124.
    To reduce the contribution of the regularizer in the early stages of training, a planner for
    $\lambda$ is used, which quadratically increases $\lambda$ at each training iteration, up to a
    given step (50k), from which it is fixed for another 100k iterations.
    The hyper-parameter $\lambda$ is chosen from the $[1 \cdot 10^{-4}, 1 \cdot 10^{-1}]$ interval.

@@

    \paragraph{Loss function.}
    During training, it is necessary to make a embeddings inner product for the relevant
    query-document pairs larger than for the irrelevant ones.
    The model uses the MultiLabelMarginLoss \cite{multiLabelMarginLoss} as loss function:
    \begin{multline}
        \mathnormal{L}(q,d_1^+,...,d_m^+,d_{m+1}^-,...,d_n^-) = \\
        \frac{1}{n} \cdot \sum_{1 \leq i \leq m,m < j \leq n}
        max(0, 1 - (Rel(q,d_i^+) - Rel(q,d_j^-)))
    \end{multline}
    where $(q,d_1^+,...,d_m^+,d_{m+1}^-,...,d_n^-)$ is one instance of the input training batch,
    \emph{q} is query, \emph{m} is quantity of relevant documents and \emph{n - m} is quantity
    of irrelevant documents\cite{RepBERT}.\\\par
    The model has a simple architecture in order to improve work efficiency.

>>>>

    \paragraph{Joint loss function.}
    The importance predictor and gating controller are trained jointly because the supervisory
    ranking signal can also be leveraged to guide the training of the gating controller:
    \begin{equation}
        L = L_{rank} + L_{exp}
    \end{equation}

@@

    This approach does not use binary gating as in SparTerm, and instead learn model (Equation
    \ref{eqn:splade:importance}) jointly optimizing ranking and regularization losses:
    \begin{equation}
        L = L_{rank-IBN} + \lambda_q L^q_{reg} + \lambda_d L^d_{reg}
    \end{equation}
    where $L_{reg}$ is a sparse regularisation ($L_1$ or $L_{FLOPS}$), $\lambda_q$ and
    $\lambda_d$ are tunable hyper-parameters to control the sparsity of the query and the
    document.

    \paragraph{Training.}
    The models are initialized with the BERT-base pre-trained models.
    Adam optimizer is selected with the learning rate $2 \cdot 10^{-5}$, linear scheduling,
    a warmup of 6000 steps and a batch size of 124.
    To reduce the contribution of the regularizer in the early stages of training, a planner for
    $\lambda$ is used, which quadratically increases $\lambda$ at each training iteration, up to a
    given step (50k), from which it is fixed for another 100k iterations.
    The hyper-parameter $\lambda$ is chosen from the $[1 \cdot 10^{-4}, 1 \cdot 10^{-1}]$
    interval.\newline

@@

    \paragraph{Loss function.}
    During training, it is necessary to make a embeddings inner product for the relevant
    query-document pairs larger than for the irrelevant ones.
    The model uses the MultiLabelMarginLoss \cite{multiLabelMarginLoss} as loss function:
    \begin{multline}
        \mathnormal{L}(q,d_1^+,...,d_m^+,d_{m+1}^-,...,d_n^-) = \\
        \frac{1}{n} \cdot \sum_{1 \leq i \leq m,m < j \leq n}
        max(0, 1 - (Rel(q,d_i^+) - Rel(q,d_j^-)))
    \end{multline}
    where $(q,d_1^+,...,d_m^+,d_{m+1}^-,...,d_n^-)$ is one instance of the input training batch,
    \emph{q} is query, \emph{m} is quantity of relevant documents and \emph{n - m} is quantity
    of irrelevant documents\cite{RepBERT}.

    \paragraph{Training.}
    BERT base model is adapted.
    It consists of 12 encoder layers with vector dimension of 768.
    The model is fine-tuned for 350k iterations with batch size of 26 and gradient accumulation
    steps of 2.
    Adam optimizer is selected with the learning rate $3 \cdot 10^{-6}$,
    $\lambda_1 = 0.9$ and $\lambda_2 = 0.999$, $L_2$ weight decay of 0.01, learning rate warmup
    over the first 10k iterations, and linear decay of the learning rate.
    Dropout probability is 0.1 on all layers.\newline

    The model has a simple architecture in order to improve work efficiency.
